Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics

### 2015-04-03 paper.tex
pequenas melhoras no texto do seccionamento

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
\title[Stability of interaction networks]{Stability in human interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\

@@

\noindent where $\{\overline{k}_{\sigma,i}\}$ is defined as:

@@

The simplification of all the compound possibilities to the small set listed above can be formalized in strict mathematical terms, but this was considered out of the scope of the present article. Notice that the exclusivist cascade is the same sectioning that an inclusivist cascade from periphery to hubs (with inverted order of sectors precedence). Compound criteria can be used to examine network sections in the case of a low number of messages, such as in the last figures of Appendix~\ref{figures}.

>>>>

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
\title[Stability of interaction networks]{Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics}% Force line breaks with \\

@@

\noindent where $\{\overline{k}_{\sigma,i}\}$ is:

@@

The simplification of all the compound possibilities to the small set listed above can be formalized in strict mathematical terms, but this was considered out of the scope for current interests. Notice that the exclusivist cascade is the same sectioning that an inclusivist cascade from periphery to hubs (with inverted order of sectors precedence). Compound criteria can be used to examine network sections in the case of a low number of messages, such as in the last figures of Appendix~\ref{figures}.
